Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-08-31 parts/intro.tex
added auto-modelling refs

The expected flood of new lens discoveries will need a similarly huge
modelling effort to reconstruct their mass distributions.  To prepare
for the challenge of massive-sample lens modelling,
\cite{2015MNRAS.447.2170K} developed a new modelling strategy,
implemented as the SpaghettiLens system.  The idea is to collaborate
with experienced members of the citizen-science community, who have
already participated in lens discovery through \SW, as well as several
other projects involving astronomical data.  The system was tested on
a sample of simulated lenses, which were part of the training and
testing set in \SW.

>>>>

The expected flood of new lens discoveries will need a similarly huge
modelling effort to reconstruct their mass distributions.
Lens-modelling robots have started to be developed
\citep{2017arXiv170807377N,2017arXiv170808842H} but so far are able to
handle only very clean systems.  For typical lenses, human input is
still needed.  With that in mind \cite{2015MNRAS.447.2170K} developed
a new modelling strategy, implemented as the SpaghettiLens system.
The idea is to collaborate with experienced members of the
citizen-science community, who have already participated in lens
discovery through \SW, as well as several other projects involving
astronomical data.  The system was tested on a sample of simulated
lenses, which were part of the training and testing set in \SW.
